Live and Let Die? (Delayed Issues not Harder to Resolve)

### 2015-08-14 data.tex
Updates from ShareLaTeX

@@

One reason to use the SEI data for the analysis of this paper is its remarkably low level of noise.
Nichols et al.~\cite{shirai14}  report that
the noise levels in the SEI TSP data are smaller than those seen
in other data sets. They found in the SEI TSP data that:\bi 
\item
4\% of the data was incorrect (e.g. nulls, illegal formats);
\item  2\% of the data has inconsistencies such as timestamps
where the stop time was before the start time;
\item 3\% of the data had data that was not credible
such as tasks listed in one day that took like than six hours.
\ei 
One explanation for this low level of noise is the TSP process.
One the guiding principles of TSP was that  people performing the work are  responsible for planning and tracking the work. That is,  all the data collected here was entered
by local developers. This data was then check by local {\em coaches} before being sent to the SEI
databases. Coaches are certified by demonstrating competent use of the TSP process with the artifacts and data.
The use of certified local coaches within each project increases the integrity of our data.

Overall, the   effort associated with adding TSP to a project is not onerous. McHale reports~\cite{mchale02}:
\bi
\item
 The time spent  tracking time, defects, and tasks requires less then 3\% of a developer's time. Weekly team meetings  require at most an hour, which is
only 2.5\% of a 40 hour work week. 
\item
Team launches and replans average about 1 day per month or 5\% planning overhead.
\ei
It is true that one staff member is needed as a ``couch'' to mentor the teams
and certify and monitor that data collection. However, one of us (Nichols) has worked with dozens of TSP teams. He reports that one  trained coach can support 4 or 6 teams (depending upon team experience).

>>>>

Overall, the   effort associated with adding TSP to a project is not onerous. McHale reports~\cite{mchale02}:
\bi
\item
 The time spent  tracking time, defects, and tasks requires less then 3\% of a developer's time. Weekly team meetings  require at most an hour, which is
only 2.5\% of a 40 hour work week. 
\item
Team launches and replans average about 1 day per month or 5\% planning overhead.
\ei
It is true that one staff member is needed as a ``coach'' to mentor the teams
and certify and monitor that data collection. However, one of us (Nichols) has worked with dozens of TSP teams. He reports that one  trained coach can support 4 or 6 teams (depending upon team experience).

@@

One reason to use the SEI data for the analysis of this paper is its remarkably low level of noise.
Nichols et al.~\cite{shirai14}  report that
the noise levels in the SEI TSP data are smaller than those seen
in other data sets. They found in the SEI TSP data that:\bi 
\item
4\% of the data was incorrect (e.g. nulls, illegal formats);
\item  2\% of the data has inconsistencies such as timestamps
where the stop time was before the start time;
\item 3\% of the data contained values that were not credible
such as tasks listed in one day that took more than six hours for a single developer.
\ei 
One explanation for this low level of noise is the TSP process.
One the guiding principles of TSP was that  people performing the work are  responsible for planning and tracking the work. That is,  all the data collected here was entered
by local developers. This data was then check by local {\em coaches} before being sent to the SEI
databases. Coaches are certified by demonstrating competent use of the TSP process with the artifacts and data.
The use of certified local coaches within each project increases the integrity of our data.
